---
title: "Where have our forests gone?"
bibliography: final_project.bib
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

This project is an analysis of world forest data according to its accessibility to the populations surrounding them. The initial data set was pulled from Kaggle, created by user @takumi_watanabe_world_2024, and references data pulled from @the_world_bank_terms_2024. Additionally, data regarding population variation was eventually pulled from the Federal Reserve Bank of St. Louis, which itself pulls information from @us_bureau_of_labor_statistics_population_2024. Similarly, socioeconomic data presented by World Economic Forum user @avery_koop_one_2022 was also extracted. These data assisted in further analyzing its effects on deforestation and its relationships with local communities. Lastly, map data was pulled from @esri_world_2022 to create a global visual that meticulously compared deforestation between every country for which forest data existed. 

You can find the code for this dashboard here:
https://github.com/Leshi-bot/DACSS_690V_Final_Project

## Column {.tabset .tabset-fade}

### Where are our forests?

```{r}
readRDS("del2Draft.rds")
```


### Who has access to our forests?

```{r}
readRDS("del1Draft.rds")
```


### How much forest is left?

```{r}
readRDS("del3Draft.rds")
```


### Where have our forests changed?

```{r}
readRDS("del4Draft.rds")
```


### References
<div id="refs"></div>